Using temperature distributions of active regions to investigate flare activity

### 2015-01-31 paper.tex
Final additions

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{lineno}
\usepackage[authoryear,round]{natbib}
\usepackage[backref]{hyperref}
\usepackage{url}
\bibliographystyle{plainnat}
\hypersetup{colorlinks=true,citecolor=cyan,urlcolor=cyan,linkcolor=blue}

@@

\titlerunning{Temperature distributions of active regions}
\authorrunning{Leonard and Morgan}
% {}{Aims}{Methods}{Results}{}
\abstract
	{}
	{To investigate whether signatures of solar flares can be seen in the temperature distributions of flaring active regions before the flares occur.}
	{A recently developed and extremely fast temperature-mapping method is used to determine the temperature of flaring active regions for the 30 minutes preceding a flare.}
	{No clear link was found between active region temperature and flare activity. However, the distribution of active region mean temperatures does suggest that a much larger sample size might show some relationship between this and peak flare flux.}
	{}
\keywords{}

@@

\begin{figure}
	\centering
		\includegraphics[width=\columnwidth]{2011-02-15T00_00_00.png}
	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00}. Temperatures are displayed on a logarithmic scale.
	\label{fig:example_tmap}
\end{figure}

@@

\begin{table}
	\centering
	\caption{Start times and associated active regions of solar flares studied during 2011-02.}
		\begin{tabular}{c|c|c}
			Date and time & GOES class & NOAA Active region \\
			\hline
			% PUT THINGS HERE
		\end{tabular}
	\label{tab:flares}
\end{table}

@@

\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Top: maximum temperature against time. Middle: running difference of maximum temperature. Bottom: difference of maximum temperature from maximum temperature at flare start time. Left: B and C class flares, denoted by orange and yellow lines, respectively. Right: M and X class flares, denoted by red and orange lines, repectively.}
	\label{fig:allars_max}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_p95/allars.png}
	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_p95}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmean/allars.png}
	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_mean}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_p5/allars.png}
	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_p5}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_min/allars.png}
	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}}
	\label{fig:allars_min}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{lineno}
\usepackage[authoryear,round]{natbib}
\usepackage[backref]{hyperref}
\usepackage{url}
\usepackage{longtable}
\bibliographystyle{plainnat}
\hypersetup{colorlinks=true,citecolor=cyan,urlcolor=cyan,linkcolor=blue}

@@

\titlerunning{Temperature distributions of active regions}
\authorrunning{Leonard and Morgan}

\abstract
	{}
	{To investigate whether signatures of solar flares can be seen in the temperature distributions of flaring active regions before the flares occur.}
	{A recently developed and extremely fast temperature-mapping method is used to determine the temperature of flaring active regions for the 30 minutes preceding a flare.}
	{No clear link was found between active region temperature and flare activity. However, the distribution of active region mean temperatures does suggest that a much larger sample size might show some relationship between this and peak flare flux.}
	{}
\keywords{}

@@

\begin{figure}
	\centering
		\includegraphics[width=\columnwidth]{2011-02-15T00_00_00.png}
	\caption{Example temperature map for the full solar corona at 2011-02-15 00:00. Temperatures are displayed on a logarithmic scale.}
	\label{fig:example_tmap}
\end{figure}

@@

\begin{longtable}{c|c|c}
	\caption{Start times and associated active regions of solar flares studied during 2011-02.}\\
		Date and time & GOES class & NOAA Active region \\
		\hline
		2011-02-01 00:09:00 & B3.0 & 11150 \\ 
		2011-02-01 05:48:00 & B1.8 & 11150 \\ 
		2011-02-01 12:27:00 & B1.4 & 11150 \\ 
		2011-02-01 23:06:00 & B4.5 & 11150 \\ 
		2011-02-02 00:27:00 & B4.1 & 11150 \\ 
		2011-02-02 02:44:00 & B1.1 & 11150 \\ 
		2011-02-02 06:14:00 & B4.1 & 11150 \\ 
		2011-02-02 10:20:00 & B2.0 & 11150 \\ 
		2011-02-03 05:51:00 & B2.6 & 11150 \\ 
		2011-02-03 17:28:00 & B2.0 & 11152 \\ 
		2011-02-04 01:37:00 & B2.0 & 11152 \\ 
		2011-02-04 03:59:00 & B1.1 & 11152 \\ 
		2011-02-04 07:29:00 & B2.7 & 11152 \\ 
		2011-02-04 12:13:00 & B9.5 & 11152 \\ 
		2011-02-04 17:30:00 & B1.3 & 11152 \\ 
		2011-02-04 19:30:00 & B6.9 & 11152 \\ 
		2011-02-05 00:03:00 & B3.6 & 11152 \\ 
		2011-02-07 10:17:00 & B1.0 & 11153 \\ 
		2011-02-07 13:31:00 & B1.9 & 11153 \\ 
		2011-02-08 01:55:00 & B2.0 & 11153 \\ 
		2011-02-08 06:48:00 & B1.9 & 11153 \\ 
		2011-02-08 08:17:00 & B1.9 & 11153 \\ 
		2011-02-08 09:10:00 & B2.4 & 11150 \\ 
		2011-02-08 10:28:00 & B1.6 & 11153 \\ 
		2011-02-08 11:34:00 & B1.9 & 11153 \\ 
		2011-02-08 14:44:00 & B5.0 & 11153 \\ 
		2011-02-08 18:46:00 & C1.0 & 11153 \\ 
		2011-02-09 00:08:00 & C1.1 & 11153 \\ 
		2011-02-09 01:23:00 & M1.9 & 11153 \\ 
		2011-02-09 05:42:00 & B4.3 & 11157 \\ 
		2011-02-09 07:23:00 & B3.2 & 11153 \\ 
		2011-02-09 10:15:00 & B5.4 & 11153 \\ 
		2011-02-09 16:19:00 & B8.6 & 11153 \\ 
		2011-02-09 18:59:00 & B2.6 & 11153 \\ 
		2011-02-09 22:07:00 & B3.3 & 11153 \\ 
		2011-02-09 22:54:00 & B7.9 & 11153 \\ 
		2011-02-10 00:00:00 & B6.3 & 11153 \\ 
		2011-02-10 03:29:00 & B5.4 & 11153 \\ 
		2011-02-10 04:39:00 & B6.0 & 11153 \\ 
		2011-02-10 06:20:00 & C1.9 & 11153 \\ 
		2011-02-10 06:55:00 & C2.0 & 11153 \\ 
		2011-02-10 09:24:00 & B4.4 & 11153 \\ 
		2011-02-10 12:28:00 & C4.7 & 11153 \\ 
		2011-02-10 13:33:00 & C2.6 & 11153 \\ 
		2011-02-10 14:38:00 & B6.7 & 11156 \\ 
		2011-02-10 20:49:00 & B5.3 & 11156 \\ 
		2011-02-12 14:30:00 & C2.6 & 11159 \\ 
		2011-02-12 19:13:00 & B5.8 & 11160 \\ 
		2011-02-12 20:23:00 & B8.9 & 11160 \\ 
		2011-02-13 00:36:00 & B8.5 & 11158 \\ 
		2011-02-13 05:59:00 & B3.2 & 11160 \\ 
		2011-02-13 07:25:00 & C1.4 & 11160 \\ 
		2011-02-13 12:29:00 & C1.1 & 11158 \\ 
		2011-02-13 13:44:00 & C4.7 & 11158 \\ 
		2011-02-13 17:28:00 & M6.6 & 11158 \\ 
		2011-02-14 02:35:00 & C1.6 & 11158 \\ 
		2011-02-14 04:29:00 & C8.3 & 11158 \\ 
		2011-02-14 06:51:00 & C6.6 & 11158 \\ 
		2011-02-14 08:39:00 & C1.8 & 11158 \\ 
		2011-02-14 11:51:00 & C1.7 & 11158 \\ 
		2011-02-14 12:41:00 & C9.4 & 11158 \\ 
		2011-02-14 13:47:00 & C7.0 & 11158 \\ 
		2011-02-14 17:20:00 & M2.2 & 11158 \\ 
		2011-02-14 19:23:00 & C6.6 & 11158 \\ 
		2011-02-14 23:14:00 & C1.2 & 11158 \\ 
		2011-02-14 23:40:00 & C2.7 & 11158 \\ 
		2011-02-15 01:44:00 & X2.2 & 11158 \\ 
		2011-02-15 14:32:00 & C4.8 & 11158 \\ 
		2011-02-15 18:07:00 & C1.7 & 11158 \\ 
		2011-02-15 19:30:00 & C6.6 & 11158 \\ 
		2011-02-15 22:49:00 & C1.3 & 11158 \\ 
		2011-02-16 01:56:00 & C2.2 & 11158 \\ 
		2011-02-16 07:35:00 & M1.1 & 11161 \\ 
		2011-02-16 09:02:00 & C9.9 & 11158 \\ 
		2011-02-16 10:25:00 & C3.2 & 11158 \\ 
		2011-02-16 11:58:00 & C1.0 & 11158 \\ 
		2011-02-16 14:19:00 & M1.6 & 11158 \\ 
		2011-02-16 15:27:00 & C7.7 & 11158 \\ 
		2011-02-16 19:29:00 & C1.3 & 11158 \\ 
		2011-02-16 20:11:00 & C1.1 & 11158 \\ 
		2011-02-16 23:02:00 & C2.8 & 11158 \\ 
		2011-02-17 01:41:00 & C6.1 & 11158 \\ 
		2011-02-17 02:46:00 & C2.3 & 11158 \\ 
		2011-02-17 04:09:00 & C1.5 & 11158 \\ 
		2011-02-17 05:33:00 & C1.0 & 11158 \\ 
		2011-02-17 06:44:00 & C1.2 & 11158 \\ 
		2011-02-17 08:09:00 & C1.2 & 11158 \\ 
		2011-02-17 09:24:00 & C1.9 & 11158 \\ 
		2011-02-17 10:25:00 & C2.6 & 11158 \\ 
		2011-02-17 12:33:00 & C2.4 & 11158 \\ 
		2011-02-17 15:49:00 & C1.3 & 11158 \\ 
		2011-02-18 01:02:00 & C1.7 & 11158 \\ 
		2011-02-18 03:20:00 & C2.0 & 11161 \\ 
		2011-02-18 04:44:00 & C4.0 & 11161 \\ 
		2011-02-18 06:27:00 & C8.5 & 11158 \\ 
		2011-02-18 09:55:00 & M6.6 & 11158 \\ 
		2011-02-18 12:59:00 & M1.4 & 11158 \\ 
		2011-02-18 14:27:00 & C4.0 & 11158 \\ 
		2011-02-18 14:57:00 & C5.0 & 11158 \\ 
		2011-02-18 18:13:00 & C3.2 & 11158 \\ 
		2011-02-19 01:33:00 & C1.3 & 11158 \\ 
		2011-02-19 02:21:00 & C1.8 & 11158 \\ 
		2011-02-19 02:56:00 & C3.4 & 11161 \\ 
		2011-02-19 06:57:00 & C2.6 & 11162 \\ 
		2011-02-19 07:40:00 & C1.9 & 11158 \\ 
		2011-02-19 08:00:00 & C8.5 & 11162 \\ 
		2011-02-19 12:20:00 & C1.1 & 11162 \\ 
		2011-02-19 14:50:00 & C1.0 & 11162 \\ 
		2011-02-19 15:24:00 & C1.5 & 11158 \\ 
		2011-02-19 16:26:00 & C1.9 & 11158 \\ 
		2011-02-19 16:39:00 & C6.1 & 11158 \\ 
		2011-02-20 00:46:00 & C1.2 & 11161 \\ 
		2011-02-20 02:45:00 & C1.4 & 11162 \\ 
		2011-02-20 03:54:00 & C1.7 & 11161 \\ 
		2011-02-20 17:46:00 & B6.2 & 11161 \\ 
		2011-02-20 19:40:00 & B6.8 & 11161 \\ 
		2011-02-20 23:00:00 & B3.2 & 11161 \\ 
		2011-02-20 23:31:00 & B5.2 & 11161 \\ 
		2011-02-21 01:41:00 & B8.8 & 11161 \\ 
		2011-02-21 02:13:00 & C4.6 & 11158 \\ 
		2011-02-21 03:10:00 & C1.8 & 11158 \\ 
		2011-02-21 04:04:00 & C1.5 & 11158 \\ 
		2011-02-21 05:00:00 & C4.1 & 11158 \\ 
		2011-02-21 09:01:00 & C2.7 & 11158 \\ 
		2011-02-21 10:00:00 & C1.8 & 11158 \\ 
		2011-02-21 18:25:00 & C1.4 & 11161 \\ 
		2011-02-22 10:33:00 & B6.5 & 11161 \\ 
		2011-02-22 12:15:00 & B3.5 & 11161 \\ 
		2011-02-22 14:34:00 & B2.7 & 11161 \\ 
		2011-02-23 09:35:00 & B3.1 & 11161 \\ 
		2011-02-23 10:24:00 & B3.7 & 11161 \\ 
		2011-02-23 11:10:00 & B6.1 & 11161 \\ 
		2011-02-23 12:15:00 & C1.2 & 11161 \\ 
		2011-02-24 02:49:00 & B3.9 & 11161 \\ 
		2011-02-24 07:23:00 & M3.5 & 11163 \\ 
		2011-02-24 17:12:00 & B8.5 & 11163 \\ 
		2011-02-25 01:38:00 & B4.8 & 11163 \\ 
		2011-02-25 03:22:00 & B4.2 & 11163 \\ 
		2011-02-25 05:15:00 & C1.4 & 11163 \\ 
		2011-02-25 05:40:00 & C1.6 & 11163 \\ 
		2011-02-25 10:53:00 & B6.2 & 11164 \\ 
		2011-02-25 17:18:00 & C1.1 & 11164 \\ 
		2011-02-25 22:29:00 & B5.2 & 11163 \\ 
		2011-02-26 00:07:00 & B4.3 & 11164 \\ 
		2011-02-26 00:54:00 & B9.0 & 11163 \\ 
		2011-02-26 05:03:00 & B8.9 & 11164 \\ 
		2011-02-26 07:32:00 & B4.5 & 11164 \\ 
		2011-02-26 08:09:00 & C1.3 & 11164 \\ 
		2011-02-26 09:35:00 & B3.7 & 11164 \\ 
		2011-02-26 14:34:00 & B8.3 & 11163 \\ 
		2011-02-26 19:20:00 & B3.9 & 11164 \\ 
		2011-02-26 20:46:00 & B4.3 & 11163 \\ 
		2011-02-26 23:23:00 & B5.7 & 11164 \\ 
		2011-02-27 00:41:00 & B7.3 & 11164 \\ 
		2011-02-27 03:49:00 & C4.2 & 11164 \\ 
		2011-02-27 05:04:00 & B2.7 & 11164 \\ 
		2011-02-27 07:55:00 & B2.8 & 11164 \\ 
		2011-02-27 14:30:00 & B6.1 & 11164 \\ 
		2011-02-27 15:47:00 & B7.2 & 11164 \\ 
		2011-02-27 17:14:00 & B2.9 & 11164 \\ 
		2011-02-27 22:21:00 & B6.8 & 11164 \\ 
		2011-02-28 01:44:00 & B5.0 & 11164 \\ 
		2011-02-28 02:10:00 & B5.0 & 11164 \\ 
		2011-02-28 04:17:00 & B7.9 & 11164 \\ 
		2011-02-28 05:24:00 & C1.7 & 11164 \\ 
		2011-02-28 06:30:00 & C1.1 & 11164 \\ 
		2011-02-28 07:01:00 & C2.0 & 11164 \\ 
		2011-02-28 07:34:00 & C2.4 & 11164 \\ 
		2011-02-28 09:38:00 & C1.5 & 11164 \\ 
		2011-02-28 10:25:00 & B5.5 & 11164
	\label{tab:flares}
\end{longtable}

@@

\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmax/allars.png}
	\caption{Change in maximum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Top: maximum temperature against time. Middle: running difference of maximum temperature. Bottom: difference of maximum temperature from maximum temperature at flare start time. Left: B and C class flares, denoted by orange and yellow lines, respectively. Right: M and X class flares, denoted by red and orange lines, repectively.}
	\label{fig:allars_max}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_p95/allars.png}
	\caption{Change in 95th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
	\label{fig:allars_p95}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplotsmean/allars.png}
	\caption{Change in mean temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
	\label{fig:allars_mean}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_p5/allars.png}
	\caption{Change in 5th percentile temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
	\label{fig:allars_p5}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=0.7\columnwidth]{tempplots_min/allars.png}
	\caption{Change in minimum temperature of the corresponding active region plotted for each flare as a function of time before the flare began. Plots and colour-coding are the same as in Figure \ref{fig:allars_max}.}
	\label{fig:allars_min}
\end{figure}
